### 1. Load the ToothGrowth data and perform some basic exploratory data analyses
```{r}
library(datasets)
library(lattice)

xyplot(len ~ dose, ToothGrowth, groups = supp, auto.key = list(columns = 1))
xyplot(len ~ dose | supp, ToothGrowth)
```

### 2. Provide a basic summary of the data.

The data represents the tooth growth given a specific supplement and a respective dosage.

### 3. Use confidence intervals and/or hypothesis tests to compare tooth growth by supp and dose. (via techniques from class)

We could take the time to answer the question about whether or not each supplement has an effect, but we can kill two birds with one stone.

In order to figure out if the supplements are effective, we will test the hypothesis that one supplement is no better than the other supplement.
This way, we will answer two questions at once:

1. If it seems like the data we got is likely if there is no **difference** in effect, we should get, at the very least, a zero within our confidence interval.
2. On the other hand, if one supplement is better than the other, we will have also demonstrated that at least one of the supplements has an effect.

```{r}
supp1 <- ToothGrowth$len[1:30]
supp2 <- ToothGrowth$len[31:60]
difference <- supp2 - supp1
mn <- mean(difference)

s <- sd(difference)
range <- mn + c(-1, 1) * qt(0.975, 29) * s/(30)
print(range); print(mn)
```

### 4. State your conclusions and the assumptions needed for your conclusions.

The above means that we can be 95% confident that the average difference is between `r range`.
Our sample average difference is `r mn`.
In addition, the 95% confidence interval does not overlap with 0, indicating a very strong likelihood that there is difference in the efficacy in the supplements.